The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-02-17 src/ms.tex
Time series and box-least-squares

\begin{itemize}
  \item Time Series sub-package (V3.1: New Box Least Squares Periodogram)
%  \item Uncertainties and Distributions
  \item ERFA module is now it’s own thing; Obliquely tie in that units
    remains in astropy
  \item ? Pytest plugin ecosystem
  \item A new SpectralCoord class for representing and transforming spectral quantities
    Velocity in Coordinates
  \item WCS API : A shared Python interface for World Coordinate Systems
        Include APE reference
\end{itemize}

@@

>>>>

\begin{itemize}
%  \item Time Series sub-package (V3.1: New Box Least Squares Periodogram)
%  \item Uncertainties and Distributions
  \item ERFA module is now it’s own thing; Obliquely tie in that units
    remains in astropy
  \item ? Pytest plugin ecosystem
  \item A new SpectralCoord class for representing and transforming spectral quantities
    Velocity in Coordinates
  \item WCS API : A shared Python interface for World Coordinate Systems
        Include APE reference
\end{itemize}

@@

\paragraph{Time series.}  From sampling a continuous variable at fixed
times to counting events binned into time windows, many different
areas of astrophysics require the manipulation of time series.  These
are often logically tables, and the new \astropysubpkg{timeseries}
sub-package extends the \astropyQTable\ class to tables of data as a
function of time, where the data can either represent samples or
averages over particular time bins.  The new classes offer a number of
special methods to manipulate time series (folding, resampling, etc.)
and to read different data formats (such as {\em Kepler} lightcurves,
etc.).

Also part of \astropysubpkg{timeseries} are common analysis routines,
including Lomb-Scargle and box-least-squares periodogrammes.
